Output Summary

### 2023-05-03 03-post-process/output-plots-children/05-length.Rmd
Consistency updates: 05-length.Rmd

```{r L_Pb_tseries-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
```

@@

```{r L_Pb_tseries-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
  )

  # draw the predicted time series
  add_tseries(est = post_summ(post, sub_index("^L_Pb_dot[year,pop]", pop = j, year = ts_yrs)),
              yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Parr Mean Length (mm)")
```

@@

```{r L_Pb-relationship, fig.width = 6, fig.height = 5}
plot_f = function(j) {

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))

  plot(1,1, type = "n", 
       # ylim = range(pred_L_Pb_lwr, pred_L_Pb_upr, L_Pb_lwr, L_Pb_upr, na.rm = T),
       ylim = L_Pb_lim,
       xlim = range(0, E_scaled_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_L_Pb_lwr ~ E_scaled_seq, col = "red", lty = 2)
  lines(pred_L_Pb_upr ~ E_scaled_seq, col = "red", lty = 2)
  lines(pred_L_Pb_mean ~ E_scaled_seq, col = "red", lwd = 2)

  # realized pairs
  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = alpha("red", 0.5))
  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = alpha("red", 0.5))
  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

xlab = paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)")
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, xlab)
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\,(mm)$"))
```

@@

```{r Delta_L_Pb_Mb-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
```

@@

```{r Delta_L_Pb_Mb-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               Delta_L_Pb_Mb_obs, main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
```

@@

```{r Delta_L_Pb_Mb-3, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # draw the realized time series
  plot_tseries(post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr \\rightarrow Smolt\\,Growth\\, Factor$"))
```

@@

```{r Delta_L_Pb_Mb-relationship, fig.width = 6, fig.height = 5}
plot_f = function(j) {

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_Delta_L_Pb_Mb_lwr, pred_Delta_L_Pb_Mb_upr, Delta_L_Pb_Mb_lwr, Delta_L_Pb_Mb_upr, na.rm = TRUE),
       ylim = Delta_L_Pb_Mb_lim,
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_Delta_L_Pb_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_Delta_L_Pb_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = alpha("red", 0.5))
  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, TeX("$Parr\\, Mean\\, Length\\, (mm)$"))
mtext(side = 2, outer = T, line = 0.25, TeX("$Parr\\, \\to\\, Smolt\\, Growth\\, Factor$"))
```

@@

```{r L_Mb-tseries-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
```

@@

```{r L_Mb-tseries-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
  )

@@

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
```

@@

```{r L_Mb-v-L_Pb, fig.width = 6, fig.height = 5}
plot_fn = function(j) {

@@

  # make a blank plot with the correct dimensions
  par(mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot(1,1, type = "n", 
       # ylim = range(pred_L_Mb_lwr, pred_L_Mb_upr, L_Mb_lwr, L_Mb_upr, na.rm = T),
       # ylim = c(75,110),
       # xlim = range(L_Pb_seq), 
       xlim = L_Pb_lim,
       ylim = L_Mb_lim,
       main = pops[j]
  )

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = alpha("salmon", 0.5))
  lines(pred_L_Mb_lwr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_L_Mb_upr ~ L_Pb_seq, col = "red", lty = 2)
  lines(pred_L_Mb_mean ~ L_Pb_seq, col = "red", lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = alpha("red", 0.5))
  points(L_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(L_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Parr Mean Length (mm)")
mtext(side = 2, outer = T, line = 0.25, "Smolt Mean Length (mm)")
```

>>>>

```{r L_Pb_tseries-1, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
  )
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Parr Mean Length (mm)")
```

@@

```{r L_Pb_tseries-2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Pb[year,pop]", year = ts_yrs, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Pb_lim
  )

  # predicted time series
  add_tseries(est = post_summ(post, sub_index("^L_Pb_dot[year,pop]", pop = j, year = ts_yrs)),
              yrs = all_yrs[ts_yrs])
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Parr Mean Length (mm)")

```

@@

```{r L_Pb-relationship, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

@@

  plot(1,1, type = "n", 
       ylim = L_Pb_lim,
       xlim = range(0, E_scaled_seq)
  )
  panel_label(pops[j], "topright")

  # expected relationship
  polygon(c(E_scaled_seq, rev(E_scaled_seq)), c(pred_L_Pb_lwr, rev(pred_L_Pb_upr)), border = NA, col = tran_cols["model"])
  lines(pred_L_Pb_mean ~ E_scaled_seq, col = main_cols["model"], lwd = 2)

  # realized pairs
  segments(E_scaled_lwr, L_Pb_mean, E_scaled_upr, L_Pb_mean, col = main_cols["model"])
  segments(E_scaled_mean, L_Pb_lwr, E_scaled_mean, L_Pb_upr, col = main_cols["model"])
  points(L_Pb_mean ~ E_scaled_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
  text(L_Pb_mean ~ E_scaled_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
  box(col = par("col.axis"))
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels(
  paste0("Eggs/WUL (", prettyNum(jags_data$E_scale, big.mark = ","), "s per km)"),
  "Parr Mean Length (mm)"
)
```

@@

```{r Delta_L_Pb_Mb-1, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Parr \u2192 Smolt Growth Factor")
```

@@

```{r Delta_L_Pb_Mb-2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  Delta_L_Pb_Mb_obs = cbind(mean = jags_data$L_Mb_obs[observable,j]/jags_data$L_Pb_obs[observable,j], lwr95 = NA, upr95 = NA)
  plot_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               obs = Delta_L_Pb_Mb_obs, label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim, pt_cex = pt_cex)
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Parr \u2192 Smolt Growth Factor")
```

@@

```{r Delta_L_Pb_Mb-3, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {
  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^Delta_L_Pb_Mb[year,pop]$", year = ts_yrs, pop = j)),
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = Delta_L_Pb_Mb_lim)

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Parr \u2192 Smolt Growth Factor")
```

@@

```{r Delta_L_Pb_Mb-relationship, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

@@

  plot(1,1, type = "n", 
       ylim = Delta_L_Pb_Mb_lim,
       xlim = range(L_Pb_seq)
  )
  panel_label(pops[j], "topright")

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_Delta_L_Pb_Mb_lwr, rev(pred_Delta_L_Pb_Mb_upr)), border = NA, col = tran_cols["model"])
  lines(pred_Delta_L_Pb_Mb_mean ~ L_Pb_seq, col = main_cols["model"], lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, Delta_L_Pb_Mb_mean, L_Pb_upr, Delta_L_Pb_Mb_mean, col = main_cols["model"])
  segments(L_Pb_mean, Delta_L_Pb_Mb_lwr, L_Pb_mean, Delta_L_Pb_Mb_upr, col = main_cols["model"])
  points(Delta_L_Pb_Mb_mean ~ L_Pb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
  text(Delta_L_Pb_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")

  box(col = par("col.axis"))

}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Parr Mean Length (mm)", "Parr \u2192 Smolt Growth Factor")
```

@@

```{r L_Mb-tseries-1, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
  )
}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Smolt Mean Length (mm)")
```

@@

```{r L_Mb-tseries-2, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

  # realized time series
  plot_tseries(est = post_summ(post, sub_index("^L_Mb[year,pop]", year = ts_yrs, pop = j)), 
               label_text = pops[j], yrs = all_yrs[ts_yrs], ylim = L_Mb_lim
  )

@@

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Brood Year", "Smolt Mean Length (mm)")
```

@@

```{r L_Mb-v-L_Pb, fig.width = p4_width, fig.height = p4_height}
plot_f = function(j) {

@@

  plot(1,1, type = "n", 
       xlim = L_Pb_lim,
       ylim = L_Mb_lim
  )

  panel_label(pops[j])

  # expected relationship
  polygon(c(L_Pb_seq, rev(L_Pb_seq)), c(pred_L_Mb_lwr, rev(pred_L_Mb_upr)), border = NA, col = tran_cols["model"])
  lines(pred_L_Mb_mean ~ L_Pb_seq, col = main_cols["model"], lwd = 2)

  # realized pairs
  segments(L_Pb_lwr, L_Mb_mean, L_Pb_upr, L_Mb_mean, col = main_cols["model"])
  segments(L_Pb_mean, L_Mb_lwr, L_Pb_mean, L_Mb_upr, col = main_cols["model"])
  points(L_Mb_mean ~ L_Pb_mean, pch = 16, col = tran_cols["model"], cex = 1.8)
  text(L_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
  box(col = par("col.axis"))

}

mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Parr Mean Length (mm)", "Smolt Mean Length (mm)")
```
